Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-19 paper.qmd
Updated Figure 14 axes label size

pbmc_proj_umap_model1 <- plot_proj(
  projected_df = projected_df, 
  model_df = model_df, 
  axes = axes, 
  circle = circle, 
  point_param = c(1.5, 0.2, "#a65628"), # size, alpha, color
  plot_limits = c(-0.65, 0.65), 
  title = "a2", 
  cex = 2, 
  is_category = FALSE)

@@

pbmc_proj_umap_model2 <- plot_proj(
    projected_df = projected_df, 
    model_df = model_df, 
    axes = axes, 
    circle = circle, 
    point_param = c(1.5, 0.2, "#a65628"), # size, alpha, color
    plot_limits = c(-1, 0.75), 
    title = "a3", 
    cex = 2, 
    is_category = FALSE)

@@

pbmc_proj_umap_model1_best <- plot_proj(
    projected_df = projected_df, 
    model_df = model_df, 
    axes = axes, 
    circle = circle, 
    point_param = c(1.5, 0.2, "#999999"), # size, alpha, color
    plot_limits = c(-0.65, 0.65), 
    title = "b2", 
    cex = 2, 
    is_category = FALSE)

@@

pbmc_proj_umap_model2_best <- plot_proj(
    projected_df = projected_df, 
    model_df = model_df, 
    axes = axes, 
    circle = circle, 
    point_param = c(1.5, 0.2, "#999999"), # size, alpha, color
    plot_limits = c(-1, 0.75), 
    title = "b3", 
    cex = 2, 
    is_category = FALSE)
```

>>>>

pbmc_proj_umap_model1 <- plot_proj(
  projected_df = projected_df, 
  model_df = model_df, 
  axes = axes, 
  circle = circle, 
  point_param = c(1.5, 0.2, "#a65628"), # size, alpha, color
  plot_limits = c(-0.65, 0.65), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_category = FALSE)

@@

pbmc_proj_umap_model2 <- plot_proj(
    projected_df = projected_df, 
    model_df = model_df, 
    axes = axes, 
    circle = circle, 
    point_param = c(1.5, 0.2, "#a65628"), # size, alpha, color
    plot_limits = c(-1, 0.75), 
    title = "a3", 
    cex = 2, 
    axis_text_size = 5,
    is_category = FALSE)

@@

pbmc_proj_umap_model1_best <- plot_proj(
    projected_df = projected_df, 
    model_df = model_df, 
    axes = axes, 
    circle = circle, 
    point_param = c(1.5, 0.2, "#999999"), # size, alpha, color
    plot_limits = c(-0.65, 0.65), 
    title = "b2", 
    cex = 2, 
    axis_text_size = 5,
    is_category = FALSE)

@@

pbmc_proj_umap_model2_best <- plot_proj(
    projected_df = projected_df, 
    model_df = model_df, 
    axes = axes, 
    circle = circle, 
    point_param = c(1.5, 0.2, "#999999"), # size, alpha, color
    plot_limits = c(-1, 0.75), 
    title = "b3", 
    cex = 2, 
    axis_text_size = 5,
    is_category = FALSE)
```
